---
title: "WUP_04"
author: "Louie A"
date: "fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
thedata<-read.csv(file="GSScsv.csv")
```

```{r eval=FALSE}
thedata <- thedata %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Mention that you intend to use chatGPT to the greatest extent possible. Give credit to chatGPT when you use it to create code in your report. Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

First we are trying to look at the data to see what we have and to figure out what code to use. So we conclude that we have a numerical type of problem


# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
# Plotting the fancy box plot
ggplot(thedata, aes(x = DEGREE, y = WORDSUM, fill = DEGREE)) +
  geom_boxplot(outlier.shape = 16, outlier.colour = "red", outlier.fill = "red",
               notch = TRUE, notchwidth = 0.5) +
  scale_fill_brewer(palette = "Set1") +
  labs(title = "Fancy Box Plot of WORDSUM by DEGREE") +
  theme_minimal()
```
So LT high school will not over lap Junior College or Graduate. High School will not over lap Graduate as well. As a Guess their are gonna be some difference between the 4.

### Numerical Descriptive Results

```{r}
favstats(WORDSUM~DEGREE,data=thedata)
```
So there is a difference with GRADUATE and LT high school, along with HIGH school.but we must do further test to see if there are a difference between the other results.
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
